fishtraits

### 2019-09-03 data-raw/web_scrape.Rmd
Add intentional time lags so dropdown menus have time to catch up with click commands.

for (i in 1:length(fid_text)) {
  #select and search the FID dropdown
  fid <- rd$findElement(using = 'css selector', "#fid-combo")
  fid$clearElement()
  #pass to search box
  fid$sendKeysToElement(list(fid_text[i]))
  #click matching one
  clickObject("#ui-id-1")

  #get list of Genus's that are now possible
  clickObject(".ui-combobox2 .ui-icon-triangle-1-s")
  genus_list <- rd$findElement('css selector', '#ui-id-2')
  genus_text <- unlist(strsplit(unlist(genus_list$getElementText()), "\n"))

  for (j in 1:length(genus_text)) {
    #select and search the Genus dropdown
    genus <- rd$findElement(using = 'css selector', "#genus-combo")
    genus$clearElement()
    genus$sendKeysToElement(list(genus_text[j]))
    #click matching one
    clickObject('#ui-id-2')

    #make sure the appropriate column boxes are checked
    columns <- rd$findElement(using = 'css selector', '#ui-accordion-ac1-header-1')
    columns$clickElement()

    #selectors for all boxes that need to be checked

>>>>

for (i in 6:length(fid_text)) {
  #select and search the FID dropdown
  fid <- rd$findElement(using = 'css selector', "#fid-combo")
  fid$clearElement()
  #pass to search box
  print(fid_text[i])
  fid$sendKeysToElement(list(fid_text[i]))
  #click matching one
  Sys.sleep(0.15)
  clickObject("#ui-id-1")

  #get list of Genus's that are now possible
  clickObject(".ui-combobox2 .ui-icon-triangle-1-s")
  Sys.sleep(0.15)
  genus_list <- rd$findElement('css selector', '#ui-id-2')
  genus_text <- unlist(strsplit(unlist(genus_list$getElementText()), "\n"))
  print(genus_text)

  for (j in 1:length(genus_text)) {
    #select and search the Genus dropdown
    genus <- rd$findElement(using = 'css selector', "#genus-combo")
    genus$clearElement()
    genus$sendKeysToElement(list(genus_text[j]))
    Sys.sleep(0.15)
    #click matching one
    clickObject('#ui-id-2')

    #make sure the appropriate column boxes are checked
    # columns <- rd$findElement(using = 'css selector', '#ui-accordion-ac1-header-1')
    # columns$clickElement()
    # 
    #selectors for all boxes that need to be checked
